Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-03-25 demystify.tex

A related reason is that you did not show enough interest in the program.
For example, your SOP did not mention any faculty or research area at the program, or you did not respond to professors interested in interviewing you (which might be considered unprofessional and burn bridges).

@@

If you think you have red flags, you should address them in your SOP or ask your letter writers to do so. 
In general, these things are rare, but they do happen and cause concern to the adcom.

>>>>

A related reason is that you did not show enough interests in the program.
For example, your SOP did not mention any faculty or research area at the program, or you did not respond to professors interested in interviewing you (which might be considered unprofessional and burn bridges).

@@

If you think you have these issues, you should address them in your SOP or ask your letter writers to do so.
In general, these things are rare, but they do happen and cause concern to the adcom.
